IIoT's need for edge computing with AI capabilities for more securely transformation into industry 4.0

### 2025-04-28 article.tex
error fixing. Ready for submit

\section{Introduction}
The grooving interconnectivity between devices, sensors and cloud systems exposes industrial networks to various cyber security threats. Industry 4.0's goal with IoT to connect all things create such great mass of data and datapoints that is being impossible by human to handle without advanced security algorithms. This article is based upon two recent articles providing insights into how technologies within big data analytics, deep learning and edge computing can strengthen IIoT security. Discussing confidentiality, integrity, authentication, access control etc.     
\newline\newline
The first paper \cite{SurveySecurity}, a "A Survey on Industrial Internet of Things Security: Requirements, Attacks, AI-Based Solutions, and Edge Computing Opportunities" by Bandar Alotaibi discuss key security challenges in IIoT ecosystems, highlighting vulnerabilities across perception (end nodes), network and application layer. It is rich in examples being a survey of many papers and promotes implementing intrusion detection systems in edge computing locations for easier findings and blocking of maliouses software.   
\newline\newline
Second paper \cite{Deeplearning} "Internet of Things Security Based on Big Data and Deep Learning" by Jian-Liang Wang and Ping Chen, focuses on how deep learning techniques can enhance IoT security.

Both papers illustrate how AI-powered solutions can create more resilient industrial networks. This article examine their findings and explore how industries can integrate big-data driven security to safeguard IIoT systems.

@@

As industries continue to implement IoT technologies the digital transformation also exposes vulnerabilities, making security a priority within Industrial IoT (IIoT). Unlike traditional IT infrastructure, IIoT environments consist of distributed devices of which many operates in remote industrial locations. This decentralization creates a wide attack surface being more difficult to monitor and defend against threats. 

@@

Attackers exploit vulnerabilities across different layers of IIoT architecture, potentially causing operational disruption, financial losses, safety hazards and more. This section explores the most prominent cyberattacks targeting IIoT systems. 

@@

The perception layer consists of various objects, such as sensors, cameras, robots and smart meters. This layer is responsible of gathering data/information, for example vibrations, heat, acceleration, or humidity. The collected data is then transmitted in the network layer to be transported to an information processing system at the edge or also referenced to as fog layer. Here follows some attacks targeting the perception layer.

@@

In a \textbf{Node Capture Attack}, the attacker physically obtain, replace or modify hardware. This act could lead to exposing sensitive information related to encryption or access keys and once the attacker got hold of this information the attacker could get control over the device and start targeting or cause harm to other devices in the network. 

@@

The network layer identifies a route for the message to reach receiver. It's a network of nodes that in them self could be data gathering and/or processing devices but they are also categorized in the network layer as gateways and routers. First receiver of messages from the perception layers devices communication in an network layer is called edge nodes. Not to be confused with edge computing which is a reference to all local computing power. Here follows some attacks targeting the network layer.   

@@

\section{The Role of AI in Industrial IoT Cybersecurity}
As IIoT networks continue to expand and cybersecurity threats comes up with new sophisticated way of intruding, machine learning will play a crucial role in detecting, preventing and mitigating attacks in IIoT environment. As stated in \cite{Deeplearning}, leveraging big data analytics and deep learning techniques to analyze network behavior and identity irregular activity helps industries respond to security threats before they escalate. 
\newline\newline
IoT botnets pose one of the threats to IIoT security, enabling large-scale cyberattacks such as DDoS attacks with remote control over compromised devices. Attackers build botnets by exploiting unprotected or misconfigured IIoT devices, turning them into a network of malicious nodes that execute coordinated attacks. In \cite{botnets} it is explored how machine and deep-learning techniques can effectively identify, predict and neutralize these threats before they cause damage. 
\newline\newline
AI-based security frameworks analyze network traffic, device behavior and communication patterns to detect anomalies linked to botnet activities. Machine learning models trained on historical attack data can recognize unusual spikes in traffic. Deep learning algorithms further enhance botnet detection by learning to distinguish normal IIoT activity from potentially compromised device behaviors, making these systems highly adaptable to new botnet variants. 
\newline\newline
One example \cite{Mirai} of how devastating IoT botnet could become was Mirai, which first emerged in 2016. Mirai targeted vulnerable IoT devices, such as IP-cameras and routers by exploiting default login credentials to gain control over them. Once infected, these devices were recruited into a massive botnet capable of executing DDoS attacks. The Mirai botnet infamously took down major websites, including Twitter, Netflix and Spotify, by overwhelming them with traffic, rendering them inaccessible. As number of IoT devices within IIoT increases a local botnet could be created by an intruder executing DDoS attacks against other critical systems in the local factory plant. 
\newline
AI-driven defense mechanism can counter similar botnet threats by employing improved threat detection, anomaly recognition, botnet identification and real-time response, strengthening industrial security.

@@

The hackers appear to have been inside the corporate network since 2014 and from there the eventually into the petrochemical plants local network. Then then got into an engineering workstation probably through flaws in operating system code or intercepting an employees login credentials. Since the workstation was communicating with plants SIS, the hackers were able to learn versions of it's system find an unknown bug in the system letting them inject code into memory that ensured they could get access to the controllers. 

>>>>

\section{Introduction}
The grooving interconnectivity between devices, sensors and cloud systems exposes industrial networks to various cyber security threats. Industry 4.0's goal with IoT to connect all things create such great mass of data and datapoints that is difficult for human to handle without advanced security algorithms. This article is based upon two recent articles providing insights into how technologies within big data analytics, deep learning and edge computing can strengthen IIoT security. Discussing confidentiality, integrity, authentication, access control etc.     
\newline\newline
The first paper \cite{SurveySecurity}, a "A Survey on Industrial Internet of Things Security: Requirements, Attacks, AI-Based Solutions, and Edge Computing Opportunities" by Bandar Alotaibi discuss key security challenges in IIoT ecosystems, highlighting vulnerabilities across perception (end nodes), network and application layer. It is rich in examples being a survey of many papers and promotes implementing intrusion detection systems in edge computing locations for easier findings and blocking of maliouses software.   
\newline\newline
Second paper \cite{Deeplearning} "Internet of Things Security Based on Big Data and Deep Learning" by Jian-Liang Wang and Ping Chen, focuses on how deep learning techniques can enhance IoT security.

Both papers illustrate how AI-powered solutions can create more resilient industrial networks. This article parrots their findings and discuss integration of automatic security algorithms to enhance IIoT systems safeguarding.

@@

As industries continue to implement IoT technologies, the digital transformation also exposes vulnerabilities, making security a priority within Industrial IoT (IIoT). Unlike traditional IT infrastructure, IIoT environments consist of distributed devices of which many operates in remote industrial locations. This decentralization creates a wide attack surface being more difficult to monitor and defend against threats. 

@@

Attackers exploit vulnerabilities across different layers of IIoT architecture, potentially causing operational disruption, financial losses, safety hazards and more. This section explores prominent cyberattacks targeting IIoT systems. 

@@

The perception layer consists of various objects, such as sensors, cameras, robots and smart meters. This layer is responsible of gathering data/information, for example vibrations, heat, acceleration, or humidity. The collected data is then transmitted in the network layer to information processing system at the edge/fog or cloud. Here follows some attacks targeting the perception layer.

@@

In a \textbf{Node Capture Attack}, the attacker physically obtain, replace or modify hardware. This act could lead to exposing sensitive information related to encryption or access keys and once the attacker get hold of this information the attacker could get control over the device and start targeting or cause harm to other devices in the network. 

@@

The network layer identifies a route for the message to reach receiver. It's a network of nodes that in themself could be data gathering and/or processing devices but they are also categorized in the network layer as gateways and routers. First receiver of messages from the perception layers devices communication in an network layer is called edge nodes. Not to be confused with edge computing which is a reference to all local computing power within the fog. Here follows some attacks targeting the network layer.   

@@

\section{The Role of AI in Industrial IoT Cybersecurity}
As IIoT networks continue to expand and cybersecurity threats comes up with new sophisticated way of intruding, machine learning will play a crucial role in detecting, preventing and mitigating attacks in IIoT environment. As stated in \cite{Deeplearning}, leveraging big data analytics and deep learning techniques to analyze network behavior and identity irregular activity helps industries respond to security threats before they escalate. 
\newline\newline
IoT botnets pose one of the threats to IIoT security, enabling large-scale cyberattacks such as DDoS attacks with remote control over compromised devices. Attackers build botnets by exploiting unprotected or misconfigured IIoT devices, turning them into a network of malicious nodes that execute coordinated attacks. In \cite{botnets} it is explored how machine and deep-learning techniques can effectively identify, predict and neutralize these threats before they cause damage. 
\newline\newline
AI-based security frameworks analyze network traffic, device behavior and communication patterns to detect anomalies linked to botnet activities. Machine learning models trained on historical attack data can recognize unusual spikes in traffic. Deep learning algorithms further enhance botnet detection by learning to distinguish normal IIoT activity from potentially compromised device behaviors, making these systems highly adaptable to new botnet variants. 
\newline\newline
One example \cite{Mirai} of how devastating IoT botnet could become is Mirai, which first emerged in 2016. Mirai targets vulnerable IoT devices, such as IP-cameras and routers by exploiting default login credentials to gain control over them. Once infected, these devices were recruited into a massive botnet capable of infecting new devices and executing DDoS attacks. The Mirai botnet infamously took down major websites, including Twitter, Netflix and Spotify, by overwhelming them with traffic, rendering them inaccessible. As number of IoT devices within IIoT increases a local botnet could be created by an intruder executing DDoS attacks against other critical systems in the local factory plant. 
\newline
AI-driven defense mechanism can counter similar botnet threats by employing improved threat detection, anomaly recognition, botnet identification and real-time response, strengthening industrial security.

@@

The hackers appear to have been inside the corporate network since 2014 and from there eventually jumped into the petrochemical plants local network. Then got into an engineering workstation probably through flaws in operating system code or intercepting an employees login credentials. Since the workstation was communicating with plants SIS, the hackers were able to learn firmware versions of SIS and find an unknown bug in the system, probably by testing the a copy of the same system with firmware version at hacker locally. This let the hacker inject code into memory that ensured they could get access to the controllers. 
